Summary of models

### 2022-09-26 Rmd/Models.Rmd
added plots

header-includes:
- \usepackage{pdflscape}
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}
---

@@

\clearpage

@@

Summary of models for fruit proportion per plant species. Binomial cbind(fruit_formado, Fruit_No). Site_ID as factor random

@@

@@

#Models _ fruit proportion 
# richnes
ta_f<-Pollinator_Plant %>%
  nest_by(Plant_gen_sp) %>%
  mutate(model = list(glmer(cbind(fruit_formado, Fruit_No)~richness + (1|Site_ID),family=binomial,data)))%>%
  summarise(broom.mixed::tidy(model)) %>%
  ungroup()

@@

ta_f<-ta_f %>%
  select(-effect, -group)  %>%
  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))

ta_f<-filter(ta_f, !term == "sd__(Intercept)")

ta_f %>% 
    kable("latex",booktabs = TRUE,digits =  4, linesep = c("","\\addlinespace")) %>% 
column_spec(6, bold = ifelse(ta_f$p.value < 0.05, T, F) )%>%
  kable_styling(position="center", latex_option="hold_position")

@@

@@

# visistation rate
ta_f2<-Pollinator_Plant %>%
  nest_by(Plant_gen_sp) %>%
  mutate(model = list(glmer(cbind(fruit_formado, Fruit_No)~visitatio_rate + (1|Site_ID),family=binomial,data)))%>%
  summarise(broom.mixed::tidy(model)) %>%
  ungroup()

@@

ta_f2<-ta_f2 %>%
  select(-effect, -group)  %>%
  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))

ta_f2<-filter(ta_f2, !term == "sd__(Intercept)")

ta_f2 %>% 
kable("latex",booktabs = TRUE,digits =  4, linesep = c("","\\addlinespace")) %>% 
column_spec(6, bold = ifelse(ta_f2$p.value < 0.05, T, F) )%>%
  kable_styling(position="center", latex_option="hold_position")

>>>>

header-includes:
- \usepackage{pdflscape}
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}

---

@@

@@

@@

```{r,echo=FALSE, warning=FALSE,message=FALSE,fig.height = 13,fig.width=15, out.width="100%"}

# replace NAs by 0
# hay especies de plantas que presentan datos de fruit y seed pero no de polinizador (durante el tiempo observado no se ve ningun polinizador )
Pollinator_Plant <- mutate_all(Pollinator_Plant, ~replace(., is.na(.), 0))

#plot
plots_fruitproportion <- Pollinator_Plant %>%
  group_by(Plant_gen_sp) %>%
  group_map(~ ggplot(.) + aes(x=richness, y=fruit_proportion) + 
   geom_point() + ggtitle(.y[[1]]))

ggarrange(plots_fruitproportion[[1]],plots_fruitproportion[[2]],plots_fruitproportion[[3]],plots_fruitproportion[[4]],plots_fruitproportion[[5]],plots_fruitproportion[[6]],plots_fruitproportion[[7]],plots_fruitproportion[[8]],plots_fruitproportion[[9]],plots_fruitproportion[[10]],plots_fruitproportion[[11]],plots_fruitproportion[[12]], ncol=3, nrow=4)

Summary of models for fruit proportion ~ pollinator richness per plant species. Binomial cbind(fruit_formado, Fruit_No), fruit formada= Fruit yes + fruit preyed + fruit dispersed. Site_ID as factor random

Note: NAs is replaced by zero. The plant species have fruit and seed data but no pollinator visiting were registered. No pollinator visit the plant species during observed time

@@

#Models _ fruit proportion 
# richnes

mod_fruitproportion<-Pollinator_Plant %>%
  nest_by(Plant_gen_sp) %>%
  mutate(model = list(glmer(cbind(fruit_formado, Fruit_No)~richness + (1|Site_ID),family=binomial,data)))%>%
  summarise(broom.mixed::tidy(model)) %>%
  ungroup()

@@

mod_fruitproportion<-mod_fruitproportion %>%
  select(-effect, -group)  %>%
  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))

mod_fruitproportion<-filter(mod_fruitproportion, !term == "sd__(Intercept)")

mod_fruitproportion %>% 
    kable("latex",booktabs = TRUE,digits =  4, linesep = c("","\\addlinespace")) %>% 
column_spec(6, bold = ifelse(mod_fruitproportion$p.value < 0.05, T, F) )%>%
  kable_styling(position="center", latex_option="hold_position")

```{r,echo=FALSE, warning=FALSE,message=FALSE, out.width="80%"}

mod_fruitproportion_glance<-Pollinator_Plant %>%
  nest_by(Plant_gen_sp) %>%
  mutate(model = list(glmer(cbind(fruit_formado, Fruit_No)~richness + (1|Site_ID),family=binomial,data))) %>%
  summarize(glance(model))%>%
  ungroup()

mod_fruitproportion_glance %>% 
 kable("latex",booktabs = TRUE, digits =  3,linesep = "",align = "lccccccc")%>%
  kable_styling(font_size = 8,full_width = F, position="center")

```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%", fig.align='center'}

# model plot
mod_fruitproportion.1 <- Pollinator_Plant %>%
  nest_by(Plant_gen_sp) %>%
  mutate(model = list(glmer(cbind(fruit_formado, Fruit_No)~richness + (1|Site_ID),family=binomial,data))) %>%
  mutate(model1 = list(ggeffects::ggpredict(model, terms = "richness"))) %>%
  mutate(plots = list(ggplot(model1, aes(x, predicted)) + geom_line() +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = .2)))

p1= mod_fruitproportion.1$plots[[1]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Asphodelus fistulosus"), aes(x =  richness, y = fruit_proportion),shape=20)+ labs(x = "richness",y="fruit proportion",subtitle = "A.fistulosus")+  theme_classic()+theme(text = element_text(size=rel(3)))

p2= mod_fruitproportion.1$plots[[2]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus crispus"), aes(x =  richness, y = fruit_proportion),shape=20)+ labs(x = "richness",y="fruit proportion",subtitle = "C.crispus")+  theme_classic()+theme(text = element_text(size=rel(3)))

p3= mod_fruitproportion.1$plots[[3]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus ladanifer"), aes(x =  richness, y = fruit_proportion),shape=20)+labs(x = "richness",y="fruit proportion",subtitle = "C.ladanifer")+  theme_classic()+theme(text = element_text(size=rel(3)))

p4= mod_fruitproportion.1$plots[[4]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus libanotis"), aes(x =  richness, y = fruit_proportion),shape=20)+ labs(x = "richness",y="fruit proportion",subtitle = "C.libanotis")+  theme_classic()+theme(text = element_text(size=rel(3)))

p5= mod_fruitproportion.1$plots[[5]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus monspeliensis"), aes(x =  richness, y = fruit_proportion),shape=20)+labs(x = "richness",y="fruit proportion",subtitle = "C.monspeliensis")+  theme_classic()+theme(text = element_text(size=rel(3)))

p6= mod_fruitproportion.1$plots[[6]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus salviifolius"), aes(x =  richness, y = fruit_proportion),shape=20)+ labs(x = "richness",y="fruit proportion",subtitle = "C.salviifolius")+  theme_classic()+theme(text = element_text(size=rel(3)))

p7= mod_fruitproportion.1$plots[[7]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Halimium calycinum"), aes(x =  richness, y = fruit_proportion),shape=20)+ labs(x = "richness",y="fruit proportion",subtitle = "H.calycinum")+  theme_classic()+theme(text = element_text(size=rel(3)))

p8= mod_fruitproportion.1$plots[[8]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Halimium halimifolium"), aes(x =  richness, y = fruit_proportion),shape=20)+ labs(x = "richness",y="fruit proportion",subtitle = "H.halimifolium")+  theme_classic()+theme(text = element_text(size=rel(3)))

p9= mod_fruitproportion.1$plots[[9]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Lavandula pedunculata"), aes(x =  richness, y = fruit_proportion),shape=20)+ labs(x = "richness",y="fruit proportion",subtitle = "L.pedunculata")+  theme_classic()+theme(text = element_text(size=rel(3)))

p10= mod_fruitproportion.1$plots[[10]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Lavandula stoechas"), aes(x =  richness, y = fruit_proportion),shape=20)+ labs(x = "richness",y="fruit proportion",subtitle = "L.stoechas")+  theme_classic()+theme(text = element_text(size=rel(3)))

p11= mod_fruitproportion.1$plots[[11]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Salvia rosmarinus"), aes(x =  richness, y = fruit_proportion),shape=20)+ labs(x = "richness",y="fruit proportion",subtitle = "S.rosmarinus")+  theme_classic()+theme(text = element_text(size=rel(3)))

p12= mod_fruitproportion.1$plots[[12]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Teucrium fruticans"), aes(x =  richness, y = fruit_proportion),shape=20)+ labs(x = "richness",y="fruit proportion",subtitle = "T.fruticans")+  theme_classic()+theme(text = element_text(size=rel(3)))

p1+p2+p3+p4+p5+p6+p7+p8+p9+p10+p11+p12

@@

```{r,echo=FALSE, warning=FALSE,message=FALSE,fig.height = 13,fig.width=15, out.width="100%"}
#plot
plots_fruitproportion_2 <- Pollinator_Plant %>%
  group_by(Plant_gen_sp) %>%
  group_map(~ ggplot(.) + aes(x=visitatio_rate, y=fruit_proportion) + 
              geom_point() + ggtitle(.y[[1]]))

ggarrange(plots_fruitproportion_2[[1]],plots_fruitproportion_2[[2]],plots_fruitproportion_2[[3]],plots_fruitproportion_2[[4]],plots_fruitproportion_2[[5]],plots_fruitproportion_2[[6]],plots_fruitproportion_2[[7]],plots_fruitproportion_2[[8]],plots_fruitproportion_2[[9]],plots_fruitproportion_2[[10]],plots_fruitproportion_2[[11]],plots_fruitproportion_2[[12]], ncol=3, nrow=4)

Summary of models for fruit proportion ~ visitation rate per plant species. Binomial cbind(fruit_formado, Fruit_No), fruit formada= Fruit yes + fruit preyed + fruit dispersed. Site_ID as factor random

@@

# visistation rate
mod_fruitproportion_2<-Pollinator_Plant %>%
  nest_by(Plant_gen_sp) %>%
  mutate(model = list(glmer(cbind(fruit_formado, Fruit_No)~visitatio_rate + (1|Site_ID),family=binomial,data)))%>%
  summarise(broom.mixed::tidy(model)) %>%
  ungroup()

@@

mod_fruitproportion_2<-mod_fruitproportion_2 %>%
  select(-effect, -group)  %>%
  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))

mod_fruitproportion_2<-filter(mod_fruitproportion_2, !term == "sd__(Intercept)")

mod_fruitproportion_2 %>% 
kable("latex",booktabs = TRUE,digits =  4, linesep = c("","\\addlinespace")) %>% 
column_spec(6, bold = ifelse(mod_fruitproportion_2$p.value < 0.05, T, F) )%>%
  kable_styling(position="center", latex_option="hold_position")

```{r,echo=FALSE, warning=FALSE,message=FALSE, out.width="80%"}

mod_fruitproportion_2_glance<-Pollinator_Plant %>%
  nest_by(Plant_gen_sp) %>%
  mutate(model = list(glmer(cbind(fruit_formado, Fruit_No)~visitatio_rate + (1|Site_ID),family=binomial,data))) %>%
  summarize(glance(model))%>%
  ungroup()

mod_fruitproportion_2_glance %>% 
 kable("latex",booktabs = TRUE, digits =  3,linesep = "",align = "lccccccc")%>%
  kable_styling(font_size = 8,full_width = F, position="center")
```

```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%", fig.align='center'}

# model plot 
mod_fruitproportion.2 <- Pollinator_Plant %>%
  nest_by(Plant_gen_sp) %>%
  mutate(model = list(glmer(cbind(fruit_formado, Fruit_No)~visitatio_rate + (1|Site_ID),family=binomial,data))) %>%
  mutate(model1 = list(ggeffects::ggpredict(model, terms = "visitatio_rate"))) %>%
  mutate(plots = list(ggplot(model1, aes(x, predicted)) + geom_line() +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = .2)))

p1= mod_fruitproportion.2$plots[[1]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Asphodelus fistulosus"), aes(x =  visitatio_rate, y = fruit_proportion),shape=20)+ labs(x = "visitation_rate",y="fruit proportion",subtitle = "A.fistulosus")+  theme_classic()+theme(text = element_text(size=rel(3)))

p2= mod_fruitproportion.2$plots[[2]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus crispus"), aes(x =  visitatio_rate, y = fruit_proportion),shape=20)+ labs(x = "visitation_rate",y="fruit proportion",subtitle = "C.crispus")+  theme_classic()+theme(text = element_text(size=rel(3)))

p3=mod_fruitproportion.2$plots[[3]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus ladanifer"), aes(x =  visitatio_rate, y = fruit_proportion),shape=20)+labs(x = "visitation_rate",y="fruit proportion",subtitle = "C.ladanifer")+  theme_classic()+theme(text = element_text(size=rel(3)))

p4= mod_fruitproportion.2$plots[[4]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus libanotis"), aes(x =  visitatio_rate, y = fruit_proportion),shape=20)+labs(x = "visitation_rate",y="fruit proportion",subtitle = "C.libanotis")+  theme_classic()+theme(text = element_text(size=rel(3)))

p5= mod_fruitproportion.2$plots[[5]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus monspeliensis"), aes(x =  visitatio_rate, y = fruit_proportion),shape=20)+ labs(x = "visitation_rate",y="fruit proportion",subtitle = "C.monspeliensis")+  theme_classic()+theme(text = element_text(size=rel(3)))

p6= mod_fruitproportion.2$plots[[6]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus salviifolius"), aes(x =  visitatio_rate, y = fruit_proportion),shape=20)+ labs(x = "visitation_rate",y="fruit proportion",subtitle = "C.salviifolius")+  theme_classic()+theme(text = element_text(size=rel(3)))

p7= mod_fruitproportion.2$plots[[7]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Halimium calycinum"), aes(x =  visitatio_rate, y = fruit_proportion),shape=20)+labs(x = "visitation_rate",y="fruit proportion",subtitle = "H.calycinum")+  theme_classic()+theme(text = element_text(size=rel(3)))

p8= mod_fruitproportion.2$plots[[8]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Halimium halimifolium"), aes(x =  visitatio_rate, y = fruit_proportion),shape=20)+ labs(x = "visitation_rate",y="fruit proportion",subtitle = "H.halimifolium")+  theme_classic()+theme(text = element_text(size=rel(3)))

p9= mod_fruitproportion.2$plots[[9]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Lavandula pedunculata"), aes(x =  visitatio_rate, y = fruit_proportion),shape=20)+labs(x = "visitation_rate",y="fruit proportion",subtitle = "L.pedunculata")+  theme_classic()+theme(text = element_text(size=rel(3)))

p10= mod_fruitproportion.2$plots[[10]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Lavandula stoechas"), aes(x =  visitatio_rate, y = fruit_proportion),shape=20)+labs(x = "visitation_rate",y="fruit proportion",subtitle = "L.stoechas")+  theme_classic()+theme(text = element_text(size=rel(3)))

p11=mod_fruitproportion.2$plots[[11]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Salvia rosmarinus"), aes(x =  visitatio_rate, y = fruit_proportion),shape=20)+ labs(x = "visitation_rate",y="fruit proportion",subtitle = "S.rosmarinus")+  theme_classic()+theme(text = element_text(size=rel(3)))

p12= mod_fruitproportion.2$plots[[12]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Teucrium fruticans"), aes(x =  visitatio_rate, y = fruit_proportion),shape=20)+labs(x = "visitation_rate",y="fruit proportion",subtitle = "T.fruticans")+  theme_classic()+theme(text = element_text(size=rel(3)))

p1+p2+p3+p4+p5+p6+p7+p8+p9+p10+p11+p12
